---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# financialDataAnalysis

<!-- badges: start -->
  [![R-CMD-check](https://github.com/ashbythorpe/financialDataAnalysis/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/ashbythorpe/financialDataAnalysis/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/ashbythorpe/financialDataAnalysis/branch/master/graph/badge.svg)](https://app.codecov.io/gh/ashbythorpe/financialDataAnalysis?branch=master)
<!-- badges: end -->

[financialDataAnalysis](https://ashbythorpe.shinyapps.io/financialDataAnalysis/) is a website which allows users to upload, score and plot data (financial or otherwise). It provides a rich default dataset describing nearly 500 stocks and over 100 features. It's forecasting section uses an advanced machine learning algorithm trained on daily and monthly data to forecast the price of a stock over time.

The website is hosted using [shinyapps.io](https://www.shinyapps.io/):
https://ashbythorpe.shinyapps.io/financialDataAnalysis/

## Installation

You can install the development version of financialDataAnalysis from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("ashbythorpe/financialDataAnalysis")
```

## Running the app locally

```{r setup}
library(financialDataAnalysis)
```

The website was built using [shiny](https://shiny.rstudio.com/). Run it by executing the following:
```{r, eval = FALSE}
financialDataAnalysis()
```

