---
title: "Review of prototype 4"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Review of prototype 4}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This is a demonstration of prototype 4 of the 'financialDataAnalysis' project.

```{r setup}
library(financialDataAnalysis)
```

There were quite a few changes made in this prototype. First of all, the website is now hosted online, meaning that you no longer have to download the package to use it:
https://ashbythorpe.shinyapps.io/financialDataAnalysis/

# Stock data

Some work was done to make the default stock data easier to use. A few unnecessary or non-useful columns were removed, and the columns were renamed to make it easier to understand what each one represents. The names of all the columns are now in [snake case](https://en.wikipedia.org/wiki/Snake_case)

```{r}
default_stock_data
```

# Price predictions

Previously, the price prediction process did not give great results. A lot of time has been spent ensuring that the predictions are now very accurate. The `predict_price()` function can be used as before.

# Data input

The file input feature now accepts a much larger range of file types:

* Rectangular files - CSV, TSV and FWF.
* Excel files - XLS, XLSX, XLSM, XLTX and XLTM.
* Stata files - DTA.
* SPSS files - SAV, ZSAV and POR.
* SAS files - SAS7BDAT, SAS7BCAT and XPT.

Compressed files - GX, BZ2, XZ and ZIP - can also be read. However, they must make their uncompressed format clear through the file name (e.g. myfile.csv.zip).

The data input section of the website also provides a short text summary of the current data.

# Stock summary

The summary of the selected stock in the predict price section has been drastically improved.

# Plots

A lot of work has been done to improve the plot section.

First of all, a new default plot has been created: a correlation heatmap:

```{r}
correlation_plot(mtcars, show_text = TRUE)
```

Secondly, the custom plot feature has been made much more useful. There are now 6 different types of plots that you can create, and each one has a much larger number of arguments to customise the plot than before.

# Settings

A settings menu was added. Admittedly, this only has one changeable setting, which allows the user to switch from interactive plots to static ones.

# Minor changes

There are also a few minor changes that, while not super noticeable at first, I believe will benefit the overall user experience.

Certain aspects of the website's look and feel were modified slightly.

Changes were made to improve the performance and speed of the website.

Tooltips were added to give information about important and/or complicated inputs.

Loading bars and spinners were added to all graphs.
