---
title: "Review of prototype 1"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Review of prototype 1}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The 'financialDataAnalysis' project was split up into 4 prototypes. This is a demonstration of of prototype 1.

```{r setup}
library(financialDataAnalysis)
```

Prototype 1 includes the following features:
* A large and rich dataset about a set of stocks, which can be freely used and analysed.
* Two models, fit on a large dataset of historic stock prices, allowing you to predict the price of a variety of stocks.

The stock data contains `r nrow(default_stock_data)` rows and `r ncol(default_stock_data)` columns. Each row represents a particular stock.

The models can be used in the following way:

Note that the shown method for generating predictions will no longer work as of prototype 4. Instead, use the [predict_price()] function.

```{r setup2, echo = FALSE}
library(generics)
library(stats)
library(tibble)
library(bonsai)
library(lubridate)
```

First we need to create a data frame to predict on. Lets use make monthly predictions, going 6 months ahead.

```{r data}
data <- tibble(
  ticker = "GOOGL",
  ref_date = seq(
    from = today(),
    to = today() + months(6),
    by = "month"
  )
)
data
```

Now lets make predictions on the data using the monthly model.

```{r predictions, eval = FALSE}
predict(monthly_stock_model, data)
```

You can also add the predictions automatically to the data you have created.

```{r augment, eval = FALSE}
augment(monthly_stock_model, data)
```
